---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/newdata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/newdata/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/newdata/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/newdata?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![CRAN status](https://www.r-pkg.org/badges/version/newdata)](https://CRAN.R-project.org/package=newdata)
<!-- badges: end -->

# newdata

## Introduction

`newdata` is an R package to generate new data frames for passing to `predict` functions.
In the new data the column or columns of interest vary across their range while the remaining columns are held constant at their reference value.

 The reference value for a factor is its first level, while the reference level for columns of other types are the mean in the case of real vectors, rounded mean in the case of logical and integer vectors and floored mean in the case of Date and POSIXct vectors.

## Demonstration

```{r}
library(ggplot2)
library(newdata)

mtcars <- datasets::mtcars

model <- lm(mpg ~ wt + hp + poly(disp,2), data = mtcars)
summary(model)

# generate a data frame across range of wt with other predictor
# variables held constant
wt <- new_data(mtcars, "wt")
head(wt)

wt <- cbind(wt, predict(model, newdata = wt, interval = "confidence"))

ggplot(data = wt, aes(x = wt, y = fit)) + 
  geom_point(data = mtcars, aes(y = mpg)) + 
  geom_line() +
  geom_line(aes(y = lwr), linetype = "dotted") +
  geom_line(aes(y = upr), linetype = "dotted") +
  ylab("mpg")

# generate a data frame across range of disp with other predictor
# variables held constant
disp <- new_data(mtcars, "disp")
head(disp)

disp <- cbind(disp, predict(model, newdata = disp, interval = "confidence"))

ggplot(data = disp, aes(x = disp, y = fit)) + 
  geom_point(data = mtcars, aes(y = mpg)) + 
  geom_line() +
  geom_line(aes(y = lwr), linetype = "dotted") +
  geom_line(aes(y = upr), linetype = "dotted") +
  ylab("mpg")
```

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/newdata)
```
# install.packages("remotes")
remotes::install_github("poissonconsulting/newdata")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/newdata/issues).

[Pull requests](https://github.com/poissonconsulting/newdata/pulls) are always welcome.

## Code of Conduct

Please note that the newdata project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

