---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/newdata.svg?branch=master)](https://travis-ci.org/poissonconsulting/newdata)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/newdata?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/newdata)
[![codecov](https://codecov.io/gh/poissonconsulting/newdata/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/newdata)

# newdata

## Introduction

`newdata` is an R package to generate new data frames for passing to `predict` functions.
In the new data the column or columns of interest vary across their range while the remaining columns are held constant at their reference value.

The reference value for a factor is its first level, while the reference level for columns of other types are the mean or rounded mean in the case of logicals, integers, Dates or POSIXcts.

## Demonstration

```{r}
library(ggplot2)
library(newdata)

mtcars <- datasets::mtcars

model <- lm(mpg ~ wt + hp + poly(disp,2), data = mtcars)
summary(model)

# generate a data frame across range of wt with other predictor
# variables held constant
wt <- new_data(mtcars, "wt")
head(wt)

wt <- cbind(wt, predict(model, newdata = wt, interval = "confidence"))

ggplot(data = wt, aes(x = wt, y = fit)) + 
  geom_point(data = mtcars, aes(y = mpg)) + 
  geom_line() +
  geom_line(aes(y = lwr), linetype = "dotted") +
  geom_line(aes(y = upr), linetype = "dotted") +
  ylab("mpg")

# generate a data frame across range of disp with other predictor
# variables held constant
disp <- new_data(mtcars, "disp")
head(disp)

disp <- cbind(disp, predict(model, newdata = disp, interval = "confidence"))

ggplot(data = disp, aes(x = disp, y = fit)) + 
  geom_point(data = mtcars, aes(y = mpg)) + 
  geom_line() +
  geom_line(aes(y = lwr), linetype = "dotted") +
  geom_line(aes(y = upr), linetype = "dotted") +
  ylab("mpg")
```

## Installation

To install the latest version from GitHub
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/newdata")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/newdata/issues).

[Pull requests](https://github.com/poissonconsulting/newdata/pulls) are always welcome.

