---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/newdata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/newdata/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/newdata/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/newdata?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![CRAN status](https://www.r-pkg.org/badges/version/newdata)](https://CRAN.R-project.org/package=newdata)
<!-- badges: end -->

# newdata

## Introduction

`newdata` is an R package to generate new data frames for passing to `predict` functions.
In the new data the column(s) of interest vary across their range while the remaining columns are held constant at their reference value.

For more information see `new_data()`.

## Demonstration

```{r}
library(ggplot2)
library(newdata)

mtcars <- datasets::mtcars

model <- lm(mpg ~ wt + hp + poly(disp, 2), data = mtcars)

# generate a data frame across range of disp with other predictor
# variables held constant
disp <- new_data(mtcars, "disp")
head(disp)

disp <- cbind(disp, predict(model, newdata = disp, interval = "confidence"))

ggplot(data = disp, aes(x = disp, y = fit)) +
  geom_point(data = mtcars, aes(y = mpg)) +
  geom_line() +
  geom_line(aes(y = lwr), linetype = "dotted") +
  geom_line(aes(y = upr), linetype = "dotted") +
  ylab("mpg")
```

## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/newdata)
```
# install.packages("remotes")
remotes::install_github("poissonconsulting/newdata")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/newdata/issues).

[Pull requests](https://github.com/poissonconsulting/newdata/pulls) are always welcome.

## Code of Conduct

Please note that the newdata project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.

