---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/poissonconsulting/newdata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/newdata/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/newdata/branch/main/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/newdata?branch=main)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![CRAN status](https://www.r-pkg.org/badges/version/newdata)](https://CRAN.R-project.org/package=newdata)
<!-- badges: end -->

# newdata

## Introduction

`newdata` is an R package to generate data frames (in the form of tibbles)
for predictive purposes.

The `xnew_data()` function varies all specified variables across their range
of the observed data as a unique ordered sequence while holding all other
variables constant at their reference values.

By default all variables are held constant at their reference value 
with their type preserved.
```{r}
library(newdata)
data <- tibble::tibble(
  a = c(1L, 3L, 6L, 10L),
  b = c(1,4.5, 8.2, 10))


xnew_data(data)
```

Naming a variable causes it to vary across its range
```{r}
library(newdata)
xnew_data(data, a)
xnew_data(data, a, obs_only = TRUE)
xnew_data(data, xnew_seq(a, obs_only = FALSE))
```
## Installation

To install the latest release version from CRAN.
```r
install.packages("newdata")
```

To install the latest development version from [r-universe](https://poissonconsulting.r-universe.dev/newdata).
```r
install.packages("newdata", repos = c("https://poissonconsulting.r-universe.dev", "https://cloud.r-project.org"))
```

To install the latest development version from [GitHub](https://github.com/poissonconsulting/newdata)
```r
# install.packages("pak", repos = sprintf("https://r-lib.github.io/p/pak/stable/%s/%s/%s", .Platform$pkgType, R.Version()$os, R.Version()$arch))
pak::pak("newdata")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/newdata/issues).

[Pull requests](https://github.com/poissonconsulting/newdata/pulls) are always welcome.

## Code of Conduct

Please note that the newdata project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
