---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/poissonconsulting/newdata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/newdata/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/newdata/branch/main/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/newdata?branch=main)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![CRAN status](https://www.r-pkg.org/badges/version/newdata)](https://CRAN.R-project.org/package=newdata)
<!-- badges: end -->

# newdata

## Introduction

`newdata` is an R package to generate new data frames for predictive purposes. 
By default, all specified variables vary across their range 
while all other variables are held constant.
The user can specify the length of each sequence, require that only
observed values are used and add new variables.

By default all variables are held constant.
```{r}
library(newdata)
data <- tibble::tibble(
  a = c(1L, 3L, 6L, 10L),
  b = c(1,4.5, 8.2, 10))


xnew_data(data)
```

Specifying a variable causes it to vary across its range.

```{r}
# FIXME: this should obs_only = FALSE by default
xnew_data(data, a)
```

The user can specify the length of each sequence.
```{r}
# FIXME: this should obs_only = FALSE by default
xnew_data(data, xnew_seq(a, length_out = 3))
```

## Installation

To install the latest release version from CRAN.
```r
install.packages("newdata")
```

To install the latest development version from [r-universe](https://poissonconsulting.r-universe.dev/newdata).
```r
install.packages("newdata", repos = c("https://poissonconsulting.r-universe.dev", "https://cloud.r-project.org"))
```

To install the latest development version from [GitHub](https://github.com/poissonconsulting/newdata)
```r
# install.packages("pak", repos = sprintf("https://r-lib.github.io/p/pak/stable/%s/%s/%s", .Platform$pkgType, R.Version()$os, R.Version()$arch))
pak::pak("newdata")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/newdata/issues).

[Pull requests](https://github.com/poissonconsulting/newdata/pulls) are always welcome.

## Code of Conduct

Please note that the newdata project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
